knitr::opts_chunk$set(echo = TRUE)

---
title: "TD4 - GGPLOT2 and Rmarkdown"
output:
  html_document:
    df_print: paged
---

### Load necessary packages
```{r}
library(ggplot2)
library(dplyr)
```

### View the diamonds dataset
```{r}
View(diamonds)
```

### Obtain a summary of the diamonds dataset
```{r}
glimpse(diamonds)
summary(diamonds)
```

### Visualize the histogram of the price variable
```{r}
ggplot(diamonds, aes(x = price)) +
  geom_histogram(bins = 20)
```
  
### Visualize the histogram of the price variable for diamonds less than $5,000
```{r}
ggplot(diamonds %>% filter(price < 5000), aes(x = price)) +
  geom_histogram(bins = 20)
```
  
### Visualize a potential correlation between the x and y variables
```{r}
ggplot(diamonds, aes(x = x, y = y)) +
  geom_point()
```
  
### Filter the dataset to improve the visualization of x and y variables
```{r}
ggplot(diamonds %>% filter(x < 20 & y < 20), aes(x = x, y = y)) +
  geom_point()
```
  
### Determine if there is a correlation between carat and price, and color the observations by clarity
```{r}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point()
```
  
### Add a single trendline to the carat-price correlation plot
```{r}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### Create a scatter plot of carat vs price for each clarity value using facet_grid()
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_point() +
  facet_grid(. ~ clarity)
```

### Visualize the distribution of price by cut using a violin plot
```{r}
ggplot(diamonds, aes(x = cut, y = price)) +
  geom_violin()
```
  
### Modify the previous histogram plot by adding an aesthetic fill by cut
```{r}
ggplot(diamonds %>% filter(price < 5000), aes(x = price, fill = cut)) +
  geom_histogram(bins = 30) +
  xlim(0, 5000)
```

### Create a bar chart of the average price of diamonds by color
```{r}
ggplot(diamonds, aes(x = color, y = price)) +
  stat_summary(fun = mean, geom = "bar")
```
